---
title: "Selective inference with scaleboot and pvclust"
author: "Hidetoshi Shimodaira"
date: "2018/12/23"
output: html_document
---

# Useful information

## websites

### scaleboot websites
- [scaleboot cran](https://cran.r-project.org/web/packages/scaleboot/index.html)
- [scaleboot homepage](http://stat.sys.i.kyoto-u.ac.jp/prog/scaleboot/)
- [scaleboot reference manual](https://cran.r-project.org/web/packages/scaleboot/scaleboot.pdf)
- [Multiscale Bootstrap using Scaleboot Package](https://cran.r-project.org/web/packages/scaleboot/vignettes/usesb.pdf)
- The source file of above vignette is [usesb.Rnw](usesb.Rnw)
- [scaleboot github](https://github.com/shimo-lab/scaleboot)

### pvclust websites
- [pvclust cran](https://cran.r-project.org/web/packages/pvclust/index.html)
- [pvclust homepage](http://stat.sys.i.kyoto-u.ac.jp/prog/pvclust/)
- [pvclut reference manual](https://cran.r-project.org/web/packages/pvclust/pvclust.pdf)
- [pvclust github](https://github.com/shimo-lab/pvclust)

### consel weibsites
- [consel homepage](http://stat.sys.i.kyoto-u.ac.jp/prog/consel/)
- [consel quick guide](http://stat.sys.i.kyoto-u.ac.jp/prog/consel/quick.html)
- [consel user guide](http://stat.sys.i.kyoto-u.ac.jp/prog/consel/doc/program.pdf)


## using the rell output in the library

### loading packages

```{r}
library(scaleboot)
library(pvclust)
data(mam15)
```

### extract results for 15 trees

```{r}
mam15.trees <- mam15.relltest[1:15]  # 15 trees
stat <- attr(mam15.trees,"stat") # likelihood
mam15.trees <- mam15.trees[order(stat)] # sort
summary(mam15.trees, k=2:3) # p-values
plot(mam15.trees[1:4]) # fitting for the best 4 trees
```